Testing Traversability of Protein Tunnels with Flexible Ligands Using Motion Planning

### 2017-06-14 paper.tex

\title*{
    Testing traversability of protein tunnels with flexible ligands using motion planning
}

\author{
    Vojt\v ech Von\' asek \and 
    Barbora Kozl\'\i kov\'a  \and 
    Adam Jur\v{c}\'\i k  \and 
    David Bend\'{a}\v{r}  \and
    Martin Saska }

\institute{
    V. Von\'{a}sek, Martin Saska \at 
    Faculty of Electrical Engineering,  
Czech Technical University in Prague, 
Technick\'a 2, 166 27, Prague 6, Czech Republic
\email{vonasek@labe.felk.cvut.cz}  
\and
B. Kozl\'{\i}kov\'{a}, A. Jur\v{c}\'{\i}k \at
Faculty of Informatics,  
Masaryk University, 
Botanick\'a 68a, 602 00 Brno, \\
\and 
D. Bedn\'a\v{r} \at
Loschmidt Laboratories, Department of Experimental Biology, Masaryk University, Brno, Czech Republic
    International Centre for Clinical Research, St. Anne’s University Hospital Brno, Brno, Czech Republic
}

@@

To present the results to chemicists ...

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{fig/trajectories-all}
\qquad & \qquad
\includegraphics[width=0.45\textwidth]{fig/trajectories-clustered-21} \\
\end{tabular}
\caption{Visualization of resulting trajectories.
Left: All trajectories colored according to whether they reached the end of the tunnel (green) or they did not (red).
Right: Trajectories clustered according to their proximity colored by distinct colors.
The different line widths represent the number of trajectories in a cluster.}
\label{fig:trajectories}
\end{figure}

@@

\begin{figure}
\centering
\caption{\label{fig::tunnel}
    TODO image of the tunnel + 1cqw
}
\end{figure}

\begin{table}
\centering
\caption{\label{tab::rrt}
    Runtime and sucess ratio of the planner
}
\input table.003.tex
\hskip 10pt
%\input table.004.tex
\end{table}

@@

\section{Conclusion }

>>>>

\title*{
    Testing Traversability of Protein Tunnels with Flexible Ligands Using Motion Planning
}

\author{
    Vojt\v ech Von\' asek \and 
    Barbora Kozl\'\i kov\'a  \and 
    Adam Jur\v{c}\'\i k  \and 
    David Bedn\'{a}\v{r}  \and
    Martin Saska }

\institute{
    V. Von\'{a}sek, Martin Saska \at 
    Faculty of Electrical Engineering,  
Czech Technical University in Prague, 
Technick\'a 2, 166 27, Prague 6, Czech Republic
\email{vonasek@labe.felk.cvut.cz}  
\and
B. Kozl\'{\i}kov\'{a}, A. Jur\v{c}\'{\i}k \at
Faculty of Informatics,  
Masaryk University, 
Botanick\'a 68a, 602 00 Brno, \\
\and 
\inst{3}
David Bedn\'{a}\v{r} \at 
Faculty of Science,
Masaryk University,
Kamenice 5, 625 00 Brno
}

@@

To present the results to chemists ...

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.4\textwidth]{fig/trajectories-all}
\qquad & \qquad
\includegraphics[width=0.4\textwidth]{fig/trajectories-clustered-21} \\
\end{tabular}
\caption{Visualization of resulting trajectories.
Left: All trajectories colored according to whether they reached the end of the tunnel (green) or they did not (red).
Right: Trajectories clustered according to their proximity colored by distinct colors.
The different line widths represent the number of trajectories in a cluster.}
\label{fig:trajectories}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{fig/protein-tunnel-gray}
\caption{\label{fig::tunnel}
    The protein 1CQW visualized using its secondary structure (gray) with its highest ranked tunnel (green) which was detected using CAVER 3.0.
}
\end{figure}

\begin{table}
\centering
\caption{\label{tab::rrt}
    Runtime and sucess ratio of the planner
}
\input table.003.tex
\hskip 10pt
\input table.004.tex
\end{table}

@@

\section{Conclusion }
In the future, we will focus on the following extensions proposed by the domain experts.
Only ligand flexibility is included in the current algorithm but the flexibility of amino acid side-chains would greatly improve the prediction. 
Moreover, incorporation of some scoring function for energy evaluation would introduce the characterization of not only geometrical but also physico-chemical properties and would further improve the prediction ability of our approach.
